What Boolean Algebras Can Teach Us About Weighted Model Counting

### 2020-06-08 paper.tex
Interface cleanup
Fix memory leak

>>>>

Notes on the implementation of the algorithm
\begin{itemize}
\item We extend the Gaifman graph to add edges when two variables occur in the
  same CPT (e.g., including the edge from $A$ to $B$ when the CPT is $\Pr(A \mid
  B)$).
\item Extra benefit: one does not need to come up with a way to turn some probability
distribution to into a fully independent one.
\item Trivial CPTs such as $\Pr(A \mid B) = \Pr(\neg A \mid B) = 0.5$, the ADDs
  of which simplify to a single number, are put in the first cluster.
\item TODO: Look into ways to theoretically justify the performance benefits (I
  have some suggestions in my notes).
\item TODO: when performing experiments, measure memory usage as well.
\item TODO: Along with comparing the (3?) encodings, I could also compare this
  to using ADDs directly on Bayesian networks.
\item TODO: Feedback: Give a concrete example of something impossible to
  represent using WMC.
\end{itemize}
